Probing the Deuteron at Very Large Internal Momenta

### 2020-10-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp.tex
updated PRL

\noindent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.

@@

\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the

@@

\noindent To estimate the contribution to the yield due to the electron interaction with the aluminum endcaps of the target cell,

@@

\noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each

@@

\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)

@@

A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 

>>>>

\indent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.

@@

\indent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the

@@

\indent To estimate the contribution to the yield due to the electron interaction with the aluminum endcaps of the target cell,

@@

\indent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each

@@

\indent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)

@@

\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 

### 2020-10-18 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated PRL

is a recoil factor \ref{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the

>>>>

is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
